### 2011-11-22 docs/architecture/architecture.tex
tweak to boxlib description

\begin{figure}[t]
\centering
\includegraphics[width=6.5in]{\archfigpath/data_loc2}
\caption[Data-centerings on the grid]
  {\label{fig:dataloc} Some of the different data-centerings:
  (a) cell-centered, (b) nodal in the $x$-direction, and (c) nodal in
  both the $x$- and $y$-directions.  Note that for nodal data, the
  integer index corresponds to the lower boundary in that direction.
  In each of these centerings, the red point has the same indices:\ (1,2).
  Not shown is the case where data is nodal in the $y$-direction only.}
\end{figure}

\maestro's gridding is handled by the BoxLib library.  The underlying
idea in BoxLib is to allow for adaptive mesh refinement (AMR)---different
regions of the domain can have different spatial resolutions.  The
domain is broken into boxes.  At the coarsest (base) level of
refinement, the entire computational domain is covered, either by one
box or broken across many boxes.  Higher levels of refinement have
finer zones (typically $2\times$).  Only a portion of the domain may
be covered by the higher levels of refinement.

\MarginPar{Nesting? ghost cells?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

On a grid, the data can be stored at cell-centers, on a face/edge, or
on the corners.  In BoxLib, data that is on an edge is termed `nodal'
in that direction (see Figure~\ref{fig:dataloc}).  Data that is on the
corners is nodal in all spatial directions.  In \maestro, the state
data (density, enthalpy, velocity, $\ldots$) is generally
cell-centered.  Fluxes are nodal in the direction they represent.
A few quantities are nodal in all directions (e.g.\ $\phi$ used in
the final velocity projection).

>>>>

\maestro's gridding is handled by the BoxLib library, which
contains the most fundamental objects used to construct parallel
block-structured AMR applications---different
regions of the domain can have different spatial resolutions.
At each level of refinement, the region covered by that level is divided
into grids, or boxes.  The entire computational domain is covered by
the coarsest (base) level of refinement, often called level $\ell=0$, either by one
grid or divided into many grids.
Higher levels of refinement have cells that are finer by a ``refinement ratio''
(typically 2).  The grids are properly nested in the sense that the union 
of grids at level $\ell+1$ is contained in the union of grids at level $\ell$.
Furthermore, the containment is strict in the sense that, except at physical 
boundaries, the level $\ell$ grids are large enough to guarantee that there is
a border at least $n_{\rm buffer}$ level $\ell$ cells wide surrounding each level
$\ell +1$ grid (grids at all levels are allowed to extend to the physical
boundaries so the proper nesting is not strict there).  
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).
\MarginPar{ghost cells?}

\begin{figure}[t]
\centering
\includegraphics[width=6.5in]{\archfigpath/data_loc2}
\caption[Data-centerings on the grid]
  {\label{fig:dataloc} Some of the different data-centerings:
  (a) cell-centered, (b) nodal in the $x$-direction, and (c) nodal in
  both the $x$- and $y$-directions.  Note that for nodal data, the
  integer index corresponds to the lower boundary in that direction.
  In each of these centerings, the red point has the same indices:\ (1,2).
  Not shown is the case where data is nodal in the $y$-direction only.}
\end{figure}
On a grid, the data can be stored at cell-centers, on a face/edge, or
on the corners.  In BoxLib, data that is on an edge is termed `nodal'
in that direction (see Figure~\ref{fig:dataloc}).  Data that is on the
corners is nodal in all spatial directions.  In \maestro, the state
data (density, enthalpy, velocity, $\ldots$) is generally
cell-centered.  Fluxes are nodal in the direction they represent.
A few quantities are nodal in all directions (e.g.\ $\phi$ used in
the final velocity projection).
